Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Proposal

    Traditionally, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous task to finish before continuing.
    % Add here a few current works that use the cloud and other distributed technologies - M
    In this research,
    we present an algorithm built as a native cloud solution, totally
    distributed, where its processes are executed asynchronously and in
    parallel. We designed the algorithm using the cloud available resources to
    distribute the processing workload among several computers or as a service
    in the cloud. This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

@@

\section{Proposal}
    \label{section.proposal}
    % Always give a unique label
    % and use \ref{<label>} for cross-references
    % and \cite{<label>} for bibliographic references
    % use \sectionmark{}
    % to alter or adjust the section heading in the running head

    In previous work, we presented an algorithm inspired by nature, where we
    used observation, analysis, and abstraction to model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes results in evolution. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.

@@

    \subsection{Proposed Solution}

        In this article, we test various strategies to generate a new population to
        replace individuals that have already died (or were discarded) due to their
        aptitude, as happens in the life cycle. We previously used to generate a new
        random set of solutions, with the cost of losing all evolution knowledge. The
        strategy we describe in this paper uses elites to take advantage of the
        historical evolution, especially the best individuals, where we look for the
        offspring of the elite set to be somewhat close to them. We use the golden
        ratio to compute the distance between new individuals in the population, making
        an improved distribution.

        We propose one promising alternative to restart the population, to solve
        extinction caused by nature's pressure in the Life Cycle algorithm: the
        projection of the historically best-found candidate solutions (Elite) towards
        the best-found candidate solution (Champion). This article proposes some
        strategies to carry out this operation, where the presented distribution
        strategy obtained the best results.

        \subsubsection{How does it work?}

@@

            This strategy is how we can calculate the projection of the historically
            best-found candidate solutions (Elite) towards the best-found candidate
            solution (Champion). To illustrate this concept we include
            Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
            and the Champion solution on the left corner, where a higher number of new
            solutions will be closer to the Champion.

>>>>

    Traditionally, bio-inspired algorithms are developed with a sequential
    (synchronous) perspective
    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
    pause for the previous task to finish before continuing.
    % Add here a few current works that use the cloud and other distributed technologies - M
    In this research,
    we present a distributed algorithm built as a native cloud solution %, totally % fully, but this is hard to maintain - M
    % distributed
    , where its processes are executed asynchronously and in
    parallel. We designed the algorithm using the cloud available resources to
    distribute the processing workload among several computers or as a service
    in the cloud. 
    % The paragraph above is to repetitive, consider removing -  M
    This strategy allows to elastically increase (or reduce) the
    computing power according to the nature of the challenge
    \cite{armbrust2010view}.

@@

    % If we are not going to add a State of the Art section, we need to mention other 
    % methods in the Introduction. - M
\section{Proposal}
    \label{section.proposal}

    In previous work, we presented an algorithm inspired by nature, where we % Reference
    % used observation, analysis, and abstraction to 
    model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

        % Start by stating the similarities with a GA, in the sense that 
        % all individuals have a genotype (chromosome)that is a list of values.  - M

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.
        % I do not like that image, is not very clear. We are confused by the 
        % similarity with Venn diagrams. Maybe is better to put boxes and arrows. - M

@@

    \subsection{Proposed Solution}
        % It is important to do a literature review for the following papers, there are 
        % other works that tackle similar problems or use it as a strategy. - M 
        In this article, we test various strategies to generate a new population to
        replace individuals that have already died (or were discarded) due to their
        aptitude, as happens in the life cycle. We previously used to generate a new
        random set of solutions, with the cost of losing all evolution knowledge. The
        strategy we describe in this paper uses elites to take advantage of the
        % Where are the elites explained? - M
        historical evolution, especially the best individuals, where we look for the
        offspring of the elite set to be somewhat close to them. We use the golden
        ratio to compute the distance between new individuals in the population, making
        an improved distribution. % Why is better? Explain. - M

        We propose one promising alternative to restart the population, to solve
        extinction caused by nature's pressure in the Life Cycle algorithm: the
        projection of the historically best-found candidate solutions (Elite) towards
        % Move the explanation of Elite to where we use the term for the first time - M
        the best-found candidate solution (Champion). This article proposes some
        strategies to carry out this operation, where the presented distribution
        strategy obtained the best results. % All this goes before they are mentioned. - M

         % \subsubsection{How does it work?}

@@

            This strategy is how we can calculate the projection of the historically
            best-found candidate solutions (Elite) towards the best-found candidate
            % You can use Elite now, we all now what it is. - M
            solution (Champion). To illustrate this concept we include
            Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
            and the Champion solution on the left corner, where a higher number of new
            solutions will be closer to the Champion.
